---
title: "EFSA Submission"
subtitle: "Data export of trace elements for EFDA submission"
---

The page presents the data export of trace elements in background sediments from the pilot database.

```{r}
library(tidyverse)

efsa_submission <- tribble(
  ~Column,            ~`Lookup`, ~Optionality, ~Table,     ~`Column Names`,                      ~`Fixed Text`, ~Missing,
  "sampleId",         NA,              "Mandatory",  "Sediment", "cruise_id + core_id + sample_id", NA,          NA,
  "recId",            "Yes",           "Mandatory",  NA,         NA,                                NA,          NA,
  "envComp",          NA,              "Mandatory",  NA,         NA,                                "marine sediment", NA,
  "pristineLoc",      NA,              "Mandatory",  NA,     NA,                        "Yes",          NA,
  "sampleLocGC",      NA,              "Mandatory",  "Core",     "ddn + dde",                       NA,          NA,
  "sampleLocCM",      NA,              "Mandatory",  "Core",     "(country) + (municipality)",                        NA,          "Yes",
  "sampleDate",       NA,              "Mandatory",  "Cruise",   "year + (month) + (date)",             NA,          "Yes",
  "traceElText",      NA,           "Mandatory",  "Parameter","(symbol)",                          NA,          "Yes",
  "traceElCode",      "Yes",              "Mandatory",  "Parameter",NA,                                NA,          NA,
  "specText",         NA,           "Mandatory",  "Parameter","(speciation)",                      NA,          "Yes",
  "specCode",         "Yes",              "Mandatory",  NA,         NA,                                NA,          NA,
  "conc",             NA,              "Mandatory",  "Sediment", "value",                           NA,          NA,
  "unitText",         NA,           "Mandatory",  "Parameter","unit",                            NA,          NA,
  "unitCode",         "Yes",              "Mandatory",  NA,         NA,                                NA,          NA,
  "weightText",       NA,           "Mandatory",  NA,         NA,                                "dw",         NA,
  "weightCode",       "Yes",              "Mandatory",  NA,         NA,                                NA,          NA,
  "methAnText",       NA,           "Mandatory",  "Parameter","method1",                         NA,          NA,
  "methAnCode",       "Yes",              "Mandatory",  NA,         NA,                                NA,          NA,
  "LOD",              NA,              "Optional",   "(LLD)",         "(lld)",                    NA,          "Yes",
  "LOQ",              NA,              "Optional",   NA,         NA,                                NA,          "Yes",
  "accLab",           NA,              "Optional",   NA,         NA,                                "No",         NA,
  "phSed",            NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "TextureSedClay",   NA,              "Optional",   "Sediment", "value",                           NA,          NA,
  "TextureSedSilt",   NA,              "Optional",   "Sediment", "value",                           NA,          NA,
  "TextureSedSand",   NA,              "Optional",   "Sediment", "value",                           NA,          NA,
  "unitText2",        NA,           "Optional",   NA,         NA,                                "%",          NA,
  "unitCode2",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "weightText2",      "Yes",           "Optional",   NA,         NA,                                NA,          NA,
  "weightCode2",      "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "ocSed",            NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "unitText3",        NA,           "Optional",   NA,         NA,                                NA,          "Yes",
  "unitCode3",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "weightText3",      "Yes",           "Optional",   NA,         NA,                                NA,          NA,
  "weightCode3",      "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "phWater",          NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "hardWater",        NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "DOC",              NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "unitText5",        NA,           "Optional",   NA,         NA,                                NA,          NA,
  "unitCode5",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "publicData",       NA,              "Optional",   NA,         NA,                                "Yes",        NA,
  "refPublication",   NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "comments",         NA,              "Optional",   NA,         NA,                                NA,        "Yes",
  "Missing recId",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing envComp",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing pristineLoc",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing sampleLoc",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing sampleDate",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing traceEl",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing spec",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing conc",        "Yes",              "Optional",   NA,         NA,                                NA,          NA,
  "Missing methAn",        "Yes",              "Optional",   NA,         NA,                                NA,          NA
)

efsa_submission_full <- efsa_submission %>%
  mutate(
    across(
      where(is.character),
      ~replace_na(.x, "")
    )
  ) %>%
  rename(c(`Source Table` = "Table", 
           `Soruce Columns` = "Column Names"))

efsa_submission <- efsa_submission_full %>%
  filter(Lookup != "Yes") %>%
  dplyr::select(-c(Lookup, Missing))

```

## Data Mapping for Submission

::: {.callout-note}
### Note on Missing Mapping

If table and column names appear in parentheses, the values are not yet available in the database but will be generated in future updates.

:::


```{r}
efsa_submission
```

## Full Data Mapping
```{r}
efsa_submission_full
```

## Data Export Method
As the EFSA submission tool is an Excel file containing embedded macros, the data must be mapped column by column rather than through a standard row‑based export. This approach ensures that the structure of the submission file is not disrupted.
